---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dpi=300,
  dev = "ragg_png",
  fig.retina = .4,
  fig.width = 6,        
  fig.height = 4.2,
  out.width = "100%"

)

library(ggplot2)
library(chrisplot)

```

# chrisplot

<!-- badges: start -->

<!-- badges: end -->

This is a collection of themes, palettes, and helper functions I use to make plots using `ggplot2`.

## Installation

I made this for myself, but if you want, you can install chrisplot like so:

``` r
# install.packages("remotes")

remotes::install_github("drcaprosser/chrisplot")
```

## Themes

```{r themes}


mtcars2 <- within(mtcars, {
  vs <- factor(vs, labels = c("V-shaped", "Straight"))
  am <- factor(am, labels = c("Automatic", "Manual"))
  cyl  <- factor(cyl)
  gear <- factor(gear)
})

p1 <- ggplot(mtcars2) +
  geom_point(aes(x = wt, y = mpg, colour = gear)) +
  labs(
    title = "Fuel economy declines as weight increases",
    subtitle = "(1973-74)",
    caption = "Data from the 1974 Motor Trend US magazine.",
    tag = "Figure 1",
    x = "Weight (1000 lbs)",
    y = "Fuel economy (mpg)",
    colour = "Gears"
  )

# theme_chris
p1 + theme_chris()

# theme_academic
p1 + theme_academic()

# Facetting 

p2 <- p1 + facet_grid(vs ~ am)

p2 + theme_chris()

p2 + theme_academic()


```

## Palettes

The package includes a series of 'optimial' colour palettes created by [Anton Tsitsulin](https://tsitsul.in/blog/coloropt/). By default `chrisplot` used a slightly reordered version of Tsitsulin's 12 colour normal palette (reordered because mostly I have plots with only a couple of categories and I like the red and blue colours better than the yellow). I also like the fancy palette. I don't really use the others but included them for completeness.

```{r palettes}
p2 <- ggplot(mtcars2) +
  geom_point(aes(x = wt, y = mpg, colour = interaction(am,cyl))) +
  labs(
    title = "Fuel economy declines as weight increases",
    subtitle = "(1973-74)",
    caption = "Data from the 1974 Motor Trend US magazine.",
    tag = "Figure 1",
    x = "Weight (1000 lbs)",
    y = "Fuel economy (mpg)",
    colour = "Transmission/Cylinders"
  ) +
  theme_academic()


# Default chris_palette (reorded opt_norm_palette_12)
p2 

# Normal palette
p2 + scale_colour_manual(values = opt_norm_palette_6)

# Bright palette
p2 + scale_colour_manual(values = opt_bright_palette)

# Dark palette
p2 + scale_colour_manual(values = opt_dark_palette)

# Fancy palette
p2 + scale_colour_manual(values = opt_fancy_palette)

# Tarnish palette
p2 + scale_colour_manual(values = opt_tarnish_palette)

```
